Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-23 apples_and_oranges.qmd
Fixed bug

#this will be important later in checking for multi arm psy studies 
check_active_dups <- df_long_for_metan %>%
  filter(new_study_id %in% cbt_fluox_esc_study_ids) %>% 
  filter (psy_or_med == 1) %>% 
  group_by(new_study_id) %>%
  filter(n() >= 3)
write.csv(check_active_dups, "check_active_dups.csv")

@@

view(list_cbt_fluox_esc_study[[1]])

@@

# apply the metareg function to the list of cbt, fluox, esc
list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)

@@

# apply the metareg function to the list of cbt, fluox, esc
list_model_1_no_wl_or_cau <- run_metaregression(list_no_wl_or_cau , model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_no_wl_or_cau <-  aggregate_model_results(list_model_1_no_wl_or_cau, condition)
aggregate_results_no_wl_or_cau <- cbind(aggregate_results_no_wl_or_cau, condition)

# now use the function to extract the coefficients
means_no_wl_or_cau <-  lapply(list_model_1_no_wl_or_cau, extract_coefficients_func)

# run the mean function for no wl
condition <- levels(list_df_simulated[[1]]$four_level_var) # for the condition argument
coef_and_se_means_no_wl_or_cau <- calculate_mean_coefs_ses(means_no_wl_or_cau, condition)
coef_and_se_means_no_wl_or_cau <- data.frame(cbind(condition,coef_and_se_means_no_wl_or_cau))

coef_and_se_means_no_wl_or_cau$n <- study_count_no_wl_or_cau_study[study_count_no_wl_or_cau_study$is_missing 
                                                     ==FALSE,]$n

@@

# apply the metareg function to the list of cbt, fluox, esc
model_1 <- as.formula(~ four_level_var)
list_model_1_cdrs_study <- run_metaregression(list_cdrs_study , model_1)

@@

# extract SMDs from the list for cbt fluox escit
means_cdrs_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)

>>>>

@@

@@

# apply the metareg function to the list of no wl
list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)

@@

# apply the metareg function to the list of no wl or cau
list_model_1_no_wl_cau <- run_metaregression(list_no_wl_cau , model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_no_wl_cau <- aggregate_model_results(list_model_1_no_wl_cau, condition)
aggregate_results_no_wl_cau <- cbind(aggregate_results_no_wl_cau, condition)

# now use the function to extract the coefficients
means_no_wl_cau <-  lapply(list_model_1_no_wl_cau, extract_coefficients_func)

# run the mean function for no wl
condition <- levels(list_df_simulated[[1]]$four_level_var) # for the condition argument
coef_and_se_means_no_wl_cau <- calculate_mean_coefs_ses(means_no_wl_cau, condition)
coef_and_se_means_no_wl_cau <- data.frame(cbind(condition,coef_and_se_means_no_wl_cau))

coef_and_se_means_no_wl_cau$n <- study_count_no_wl_cau_study[study_count_no_wl_cau_study$is_missing 
                                                     ==FALSE,]$n

@@

# apply the metareg function to the list of cdrs studies
model_1 <- as.formula(~ four_level_var)
list_model_1_cdrs_study <- run_metaregression(list_cdrs_study , model_1)

@@

# extract SMDs from the list for cdrs
means_cdrs_study <-  lapply(list_model_1_cdrs_study, extract_coefficients_func)
